---
title: "Yelp_Report"
author: "Laura"
date: "12/7/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE)
pacman::p_load(
tidyverse,
magrittr,
knitr,
jsonlite,
lme4,
arm,
loo,
car
)
```

## Introduction
From the Yelp Data Set Challenge, I choose the business data for this project. The goal of this project is to see the association between restaurant's attributes(such as the ambience of restauran,noise level,parking availability..etc), categories(such as cuisine type and also serving type) with their rating stars.
For the multilevel modeling, I will use city and state as random effects and to compare the difference of the outcome between when using only state and use both state and city as random effects. This project will also explained the fixed effect of the model.
```{r,echo = FALSE}
# read data
setwd("/Users/laura/Desktop/BU/Course/678/Midterm_Project_2019/MA_678_Midterm_Project_Yelp-Challenge")
parentwd <- getwd()
setwd(dir = "./yelp_dataset")

## read --- Business
yelp_business <- stream_in(file("business.json"),verbose = FALSE)
b_flat <-jsonlite::flatten(yelp_business)

setwd(parentwd)
rm(parentwd)

```

## Data Preparation
### Clean Data
    - Choosed all restaurant data
    - Choosed restaurant with reviews more than 30 reviews
    - Cleaned data, deleted all NA rows also rows with all attributes with NA values
    - Select potential variables
```{r pressure, echo=FALSE}

## select restaurant data
all_restaurant <- b_flat[str_detect(b_flat$categories,pattern = "Restaurants"),]

## delete Toronto

## select data with reviews > 30
review_30plus <- all_restaurant[all_restaurant$review_count>30,]
# colnames(review_30plus)

## check NA columns

na.check <- function(x){

   na_count <-sapply(x, function(y) sum(length(which(is.na(y)))))
   na_count_df <- data.frame(na_count,col.n=seq(1:length(na_count)))
    return(View(na_count_df))
}

check <- apply(review_30plus, 2, function(x) any(is.na(x)))
# names(check[array(check)])

na_count <-sapply(review_30plus, function(y) sum(length(which(is.na(y)))))

na_count_df <- data.frame(na_count,col.n=seq(1:length(na_count)))


## delete all NA rows
all_na_rows <- apply(review_30plus, 1, function(x) all(is.na(x)))
review_30plus_clean <- review_30plus[!all_na_rows,]

## delete all attributes = NA rows
att_all_na <- apply(review_30plus_clean[,13:51], 1, function(x) all(is.na(x)))
review_30plus_clean.2<- review_30plus_clean[!att_all_na,]

## select columns
bs_select <-review_30plus_clean.2[,c(1:12,16,17,18,20,21,22,24,25,26,27)]
bs_clean <- bs_select


## all attributes

# bs_select <- na.omit(review_30plus[,c(1:12,16,17,18,20,21,22,24,25,26,27)])
# na.check(bs_clean)
## only one restaurant in TX, exclude TX
bs_clean <-bs_select[-which(bs_select$state=="TX"),]
# View(head(bs_clean,5))
# dplyr::mutate(bs_clean,)

```

### Modify Data
    -Modify missing data in the subset dataset and add new columns as n_parks, Caters, Take out, PriceRange, OutdoorSeating, HasTV, WiFi,Alcohol,
     romantic, intimate, classy, hipster, divey, touristy, trendy, upscale, casual,
     Asian, American, Nightlife, Breakfast_Brunch, Italian,Mexican, Mediterranean
### Variable Explanation
*   `business_id` : Business(retaurant)'s unique ID
*   `name`: Business(retaurant)'s name
*   `city`: City of the business located
*   `state`: State of the business located
*   `postal_code` : Post code of the business
*   `stars`: The rating stars of the business, rounded to half-stars
*   `review_count`: Number of reviews
*   `is_open`: 0 or 1 for closed or open
*   `n_parks`: Number of ways of parking the restauran is avaliable
*   `Caters`: 0 or 1 for without or with caters
*   `TakeOut`: 0 or 1 for can takeout or can't takeout
*   `PriceRange`: 1-4 for low to high price level
*   `OutdoorSeating`: 0 or 1 for unavailable or available for ourdoor seating
*   `HasTV`: 0 or 1 for unavailable or available for TV
*   `NoiseLevel`: Categorized as average, loud, quiet, very_loud
*   `WiFi`: no or yew for unavailable or available for WiFi
*   `WiFi`: 0 or 1 for unavailable or available for WiFi
*   `Alcohol`: Categorized the restauran as avaliable for beer_and_wine,full_bar or none
*   `Ambience`: Columns named as romantic, intimate, classy, hipster, divey, touristy, trendy, upscale, casual. Each column with 0 or 1 value, 
                indicates whether has the corresponsive attributes or not
*   `Categories`: Columns named as Asian, American, Nightlife, Breakfast_Brunch, Italian,Mexican, Mediterranean. Each column with 0 or 1 value, 
                indicates whether has the corresponsive attributes or not

```{r,echo = FALSE}

# n_parks
bs_new <- bs_clean %>% mutate(n_parks=str_count(bs_clean$attributes.BusinessParking,pattern = "True"))
bs_new$n_parks[is.na(bs_new$n_parks)] <- 0

# Caters

bs_new <- mutate(bs_new,Caters = if_else(attributes.Caters=="True",1,0,missing = 0))

# Take out
bs_new <- mutate(bs_new,TakeOut = if_else(attributes.RestaurantsTakeOut =="True",1,0,missing = 0))
# sum(is.na(bs_new$TakeOut))

# Price Range
# delete NA and None rows

bs_new <- bs_new[-which(bs_new$attributes.RestaurantsPriceRange2=="None"),]
bs_new <- bs_new[!is.na(bs_new$attributes.RestaurantsPriceRange2),]
bs_new$PriceRange <- bs_new$attributes.RestaurantsPriceRange2

# OutdoorSeating
bs_new <- mutate(bs_new,OutdoorSeating = if_else(attributes.OutdoorSeating =="True",1,0,missing = 0))

# HasTV
bs_new <- mutate(bs_new,HasTV = if_else(attributes.HasTV =="True",1,0,missing = 0))

# NoiseLevel
bs_new$NoiseLevel <- str_remove_all(bs_new$attributes.NoiseLevel, "u'")
bs_new$NoiseLevel <- str_remove_all(bs_new$NoiseLevel, "'")
bs_new <- bs_new[-which(bs_new$NoiseLevel=="None"),]
bs_new <- bs_new[!is.na(bs_new$NoiseLevel),]

# WiFi
bs_new$WiFi <- str_remove_all(bs_new$attributes.WiFi, "u'")
bs_new$WiFi <- str_remove_all(bs_new$WiFi, "'")
## replace wifi na with no
bs_new$WiFi[is.na(bs_new$WiFi)] <- "no"
## replace wifi none with no
bs_new$WiFi[bs_new$WiFi=="None"] <- "no"
## combine paid wifi with free wifi to yes
bs_new$WiFi[or(bs_new$WiFi=="free",bs_new$WiFi=="paid")] <- "yes"

# Alcohol
bs_new$Alcohol <- str_remove_all(bs_new$attributes.Alcohol, "u'")
bs_new$Alcohol <- str_remove_all(bs_new$Alcohol, "'")
bs_new <- bs_new[!is.na(bs_new$Alcohol),]
bs_new$Alcohol[bs_new$Alcohol=="None"] <- "none"

# Ambience
bs_new <- bs_new[!is.na(bs_new$attributes.Ambience),]
bs_new <- bs_new[-which(bs_new$attributes.Ambience=="None"),]

my_replace <- function(var1){
    res <- str_replace_all(var1,pattern = "'",replacement = '"')
    res <- str_replace_all(res,pattern = "False",replacement = "0")
    res <- str_replace_all(res,pattern = "True",replacement = "1")
    return(res)
}

replace_all <- function(df){
    return(sapply(df,FUN = my_replace))
    ## test_apply <- replace_all(test)
}


reconstruct_df <- function(l){
    null_row <- data.frame(t(c(0,0,0)))
    colnames(null_row) <- c("romantic","intimate","classy")
    for(i in 1:length(l)){
        name <-  dimnames(sapply(l[i],FUN=fromJSON))[[1]]
        #print(dt_temp)
        #print(colnames(dt_temp))
        #print(length(colnames(dt_temp)))
     #   print(i)
        if(i<2){
            val <-  unlist(sapply(l[i],FUN=fromJSON))
            dt_temp <- as.data.frame(t(as.matrix(val)))
            colnames(dt_temp) <- name
            dt <- dt_temp
        } else if(!is.null(name) ){
            val <-  unlist(sapply(l[i],FUN=fromJSON))
            dt_temp <- as.data.frame(t(as.matrix(val)))
            colnames(dt_temp) <- name
            dt <- dplyr::bind_rows(list(dt,dt_temp))
        }else {
            dt<- dplyr::bind_rows(list(dt,null_row))
        }
    }
    return(dt)
}

bs_new_colname <- data.frame(colnames(bs_new))
bs_new_2 <- bs_new[,c(1:12,19,23:31)]


Ambience <- as.data.frame(bs_new_2$attributes.Ambience)
bs_new_3 <- replace_all(Ambience)
bs_new_4 <- reconstruct_df(bs_new_3)

# replace na function
replace_na <- function(x){
    x[is.na(x)] <- 0
    return(x)
}

# replace ambience na
bs_new_4_c <- as.data.frame(sapply(bs_new_4, replace_na))
# check how many labels of each ambience
# apply(bs_new_4_c,2,sum)

bs_new_5 <- as.data.frame(cbind(bs_new_2,bs_new_4_c))

bs_new5_colname <- data.frame(colnames(bs_new_5))

c <- colnames(bs_new_5[,c(23:31)])

# for (i in 1:length(c)){
#     c[i] <- paste("Ambience.",c[i],sep = "")
# }
# colnames(bs_new_5)[23:31] <- c

# head_bs_new_5 <- head(bs_new_5,20)

bs_model <- bs_new_5

#bs_model <- bs_model[-which(bs_model$state=="TX"),]

bs_model2 <- bs_model # back up bs_model df

bs_model2 <- bs_model2[,-c(13)]

    
bs_model2%<>%dplyr::mutate_if(.predicate = is.character,.funs = factor)
# summary(bs_model2)

strings_asian <- c("Japanese", "Chinese", "Korean", "Sushi", "Asian Fusion", "Vietnamese","Thai")
strings_nightlife <- c("Nightlife")
strings_american <- c("American")
strings_Mediterranean <- c("Mediterranean","Greek")
strings_bb <- c("Breakfast & Brunch")

bs_model2 %<>% mutate(Asian= if_else(str_detect(categories,paste(strings_asian, collapse = "|"))==TRUE,1,0),
                                  American = if_else(str_detect(categories,paste(strings_american, collapse = "|"))==TRUE,1,0),
                                  Italian = if_else(str_detect(categories,"Italian")==TRUE,1,0),
                                  Mexican = if_else(str_detect(categories,"Mexican")==TRUE,1,0),
                                  Mediterranean = if_else(str_detect(categories,paste(strings_Mediterranean, collapse = "|"))==TRUE,1,0),
                                  Nightlife = if_else(str_detect(categories,paste(strings_nightlife, collapse = "|"))==TRUE,1,0),
                                  Breakfast_Brunch = if_else(str_detect(categories,paste(strings_bb, collapse = "|"))==TRUE,1,0))

#head(bs_model2,5)

```

## EDA
#### Restaurant observations in each states, grouped by is_open, 0 for closed, 1 for open
```{r}
ggplot(bs_model2) + geom_bar(aes(x=state,y= (..count..)/sum(..count..),fill=state))+
    labs(y = "Percent",x="State")+scale_y_continuous(labels = scales::percent)+ facet_wrap(~factor(is_open))

```
As we can see in this data set, 26% of data are from Arizona, 20% from Nevada and 20% from Ontario (Canada). Most of the restaurants in the dataset are open.

#### Rating Distributions in all state
```{r}
ggplot(bs_model2,aes(x=stars)) + geom_bar(aes(color=state,fill=state)) +labs(y = "Counts",x="Stars")
ggplot(bs_model2,aes(x=stars)) + geom_bar(aes(color=state,fill=state)) + facet_wrap(~factor(state))+labs(y = "Counts",x="Stars")
```
As we can see from the plot, the overall stars distribution are concentrated on 3.5-4 scale.
From each state, we can see in AZ,NV and OH, the stars are concentrated on score 4, and in ON the score is more concentrated on 3.5.

##### Rating Distributions in all state in different attributes 
We try to see how different attributs of the restaurant contribute the influence to the rating scores.
```{r}
## Alcohol
ggplot(bs_model2,aes(x=stars)) + geom_bar(aes(color=state,fill=state)) + facet_wrap(~Alcohol) + ggtitle("Alcohol")

## HasTV
ggplot(bs_model2,aes(x=stars)) + geom_bar(aes(color=state,fill=state)) + facet_wrap(~HasTV)+ ggtitle("HasTV")

## PriceRange
ggplot(bs_model2,aes(x=stars)) + geom_bar(aes(color=state,fill=state)) + facet_wrap(~factor (PriceRange)) + ggtitle("PriceRange")

## Ourdoor Seating
ggplot(bs_model2,aes(x=stars)) + geom_bar(aes(color=state,fill=state)) + facet_wrap(~factor (OutdoorSeating))+
ggtitle("Outdoor Seating")

## Take Out
ggplot(bs_model2,aes(x=stars)) + geom_bar(aes(color=state,fill=state)) + facet_wrap(~factor (TakeOut))+
ggtitle("Take Out")

## Caters
ggplot(bs_model2,aes(x=stars)) + geom_bar(aes(color=state,fill=state)) + facet_wrap(~factor (Caters))+
ggtitle("Caters")

```
From above plots, we can see that the overall star distribution in each cateogries of the attributes didn't show much difference, however, we still can see the star distribution differences in difference state. 

#### Rating stars in different types of cuisine- Asian, American, Mediterranean, Italian, Mexican
We want to see if the rating distribution would be different in different restaurant categoires.
```{r}

strings_asian <- c("Japanese", "Chinese", "Korean", "Sushi", "Asian Fusion", "Vietnamese","Thai")
strings_nightlife <- c("Nightlife")
strings_american <- c("American")
strings_Mediterranean <- c("Mediterranean","Greek")
strings_bb <- c("Breakfast & Brunch")

## Asian
queries_asian <- bs_model2 %>% 
  filter(str_detect(bs_model2$categories, paste(strings_asian, collapse = "|")))
## Nightlife
queries_nightlife <- bs_model2 %>% 
  filter(str_detect(bs_model2$categories, paste(strings_nightlife, collapse = "|")))
## American
queries_american <- bs_model2 %>% 
  filter(str_detect(bs_model2$categories, paste(strings_american, collapse = "|")))
## Mediterranean
queries_Mediterranean <- bs_model2 %>% 
  filter(str_detect(bs_model2$categories, paste(strings_Mediterranean,collapse = "|")))
## Breakfast & Brunch
queries_bb <- bs_model2 %>% 
  filter(str_detect(bs_model2$categories, paste(strings_bb, collapse = "|")))
## Italian
queries_italian <- bs_model2 %>% 
  filter(str_detect(bs_model2$categories, "Italian"))
## Mexican
queries_mexican <- bs_model2 %>% 
  filter(str_detect(bs_model2$categories, "Mexican"))

ggplot(queries_asian) + geom_bar(aes(x=stars,color=state,fill=state)) +
    ggtitle("Asian")## asian

ggplot(queries_american) + geom_bar(aes(x=stars,color=state,fill=state))+
    ggtitle("American")## american

ggplot(queries_Mediterranean) + geom_bar(aes(x=stars,color=state,fill=state))+
    ggtitle("Mediterranean")

ggplot(queries_italian)+ geom_bar(aes(x=stars,color=state,fill=state))+
    ggtitle("Italian")

ggplot(queries_mexican)+ geom_bar(aes(x=stars,color=state,fill=state))+
    ggtitle("Mexican")
```
As we can see Mediterranean and Italian food restaurant are more concentrated on 4 stars. Asian and American food restaurant are more concentrated on 3.5 stars. Mexican food restaurant are distributed more equally on 3.5 and 4 stares. So maybe the different cuisine may have inflence on the rating stars.

#### Rating stars for categories tagged as Nightlife and Breakfast & Brunch
```{r}

ggplot(queries_nightlife) + geom_bar(aes(x=stars,color=state,fill=state))+
    ggtitle("Nightlife")## Nightlife

ggplot(queries_bb) + geom_bar(aes(x=stars,color=state,fill=state))+
    ggtitle("Breakfast & Brunch")
```
For restaurant categorized as Nightlife and Breakfast & Brunch. We can see that for Nightlife, the difference between sore 3.5 and 4 are not that much, however, for Breakfast & Brunch, scores are more concentrated on 4.

## Modeling
We are trying to see how strong the association of each factors has with the restaurant ratings.
First, we use the stepwise regression (or stepwise selection) to find the subset of variables in the data set resulting in the best performing model, that is a model that lowers prediction error.
```{r}
aic_table <- bs_model2[,c(4,5,9:11,13:37)]
fit_base <- lm(data = aic_table,stars~.)
bic_model <- step(lm(data = aic_table,formula = stars~1),direction = "forward",scope = formula(fit_base),k = log(nrow(aic_table)),trace = 0)
bic_model$call
```
From the above result, we choose NoiseLevel , review_count, trendy, Caters, 
    state, hipster, intimate, Alcohol,  Mediterranean, n_parks,
    classy, casual, PriceRange, divey, American, touristy,
    is_open, Nightlife, romantic, Italian, TakeOut, Breakfast_Brunch as independent varaibles

#### Fit lmer model to treat state as group
Then we use lemr using state as group to fit the model-fit1
```{r,echo=TRUE}

fit1 <-  lmer (data= bs_model2, stars ~ NoiseLevel + review_count + trendy + Caters + hipster + intimate + Alcohol + Mediterranean + n_parks + classy + casual + PriceRange + divey + American + touristy + 
    is_open + Nightlife + romantic + Italian + TakeOut + Breakfast_Brunch + (1|state))
display(fit1)
summary(fit1)
```

#### Fit lmer model to treat state and city as group 
Try to use both city and state as group 
```{r,echo=TRUE}
fit2 <-  lmer (data= bs_model2, stars ~ NoiseLevel + review_count + trendy + Caters + hipster + intimate + Alcohol + Mediterranean + n_parks + classy + casual + PriceRange + divey + American + touristy + 
    is_open + Nightlife + romantic + Italian + TakeOut + Breakfast_Brunch + (1|state) + (1|city))
display(fit2)
summary(fit2)
```
From the model we can see that, the Noiselevel, Alcohol, American restaurant, touristy, and TakeOut will have negtive influence of the rating stars, among them NoiseLevel as very_loud is the most significant one. Among all positive influence, review_count will be the most significant one.

##  Model Validation
#### AIC check
```{r}
AIC(fit1,fit2)
```
As can see from the result, using City and State as random effect improved the model.

#### Model use State as Random Effect
* Red plot is the observation value and the blue plot is for the prediction.
```{r fig.align="center"}
sim <- simulate(fit1,use.u=T,newdata=bs_model2)

fit_df1 <- cbind(bs_model2[,c("city","state","stars")],pred=sim$sim_1)
fit_df1$resid_pred <- fit_df1$stars-fit_df1$pred
fit_df1%<>%dplyr::mutate(pred2 = round(pred/0.5)*0.5,resid_pred2 = stars - pred2)


# ggplot(fit_df1)+geom_point()+aes(x=pred,y=resid_pred)+geom_hline(yintercept=0,lty="dashed")

ggplot(fit_df1) + geom_density(aes(x= stars),fill="red",alpha = .3) + geom_density(aes(x= pred2),fill="blue",alpha = .3) + ggtitle("Set State as Random Effect")

ggplot(fit_df1) + geom_density(aes(x= stars),fill="red",alpha = .3) + geom_density(aes(x= pred),fill="blue",alpha = .3) + facet_wrap(~state)+
ggtitle("Set State as Random Effect - By State")
```


#### Model use State and City as Random Effect
* Red plot is the observation value and the blue plot is for the prediction
```{r fig.align="center"}
sim2 <- simulate(fit2,use.u=T,newdata=bs_model2)

fit_df2 <- cbind(bs_model2[,c("city","state","stars")],pred=sim2$sim_1)
fit_df2$resid_pred <- fit_df2$stars-fit_df2$pred
fit_df2%<>%dplyr::mutate(pred2 = round(pred/0.5)*0.5,resid_pred2 = stars - pred2)

# ggplot(fit_df1)+geom_point()+aes(x=pred,y=resid_pred)+geom_hline(yintercept=0,lty="dashed")

ggplot(fit_df2) + geom_density(aes(x= stars),fill="red",alpha = .3) + geom_density(aes(x= pred2),fill="blue",alpha = .3) + ggtitle("Set State and City as Random Effect")

ggplot(fit_df2) + geom_density(aes(x= stars),fill="red",alpha = .3) + geom_density(aes(x= pred),fill="blue",alpha = .3) + facet_wrap(~state)+
ggtitle("Set State and City as Random Effect - By State")
```

From the plot we can see the multilevel model will pool the predicted value more toward 3.5. It will pull up the value of lower scores and will pull down the value of higher scores.
For each state fitting, the effect can also see from each state.

<!-- #### Validate Fix-effect for model fit1 -->
<!-- ```{r} -->
<!--  a <- fixef(fit1) -->
<!--  conf <- confint(fit1) -->
<!--  b <- conf[-1:-2,] -->
<!--  dt <- data.frame(Value= a, -->
<!--                   low=b[,1], -->
<!--                   up=b[,2], -->
<!--                   index=rownames(b)) -->
<!--  dtn <- dt[-1,] -->
<!--  ggplot(dtn,aes(y=index,x=Value,xmin=low,xmax=up)) + -->
<!--      geom_point() + geom_errorbarh() -->


<!-- # rr1 <- ranef(fit1) -->
<!-- # dd <- as.data.frame(rr1) -->
<!-- #  -->
<!-- # ggplot(dd,aes(y=)) -->
<!-- ``` -->

#### Validate Fix-effect for model fit2
```{r}
a2 <- fixef(fit2)
 conf2 <- confint(fit2)
 b2 <- conf2[-1:-3,]
 dt2 <- data.frame(Value= a2,
                  low=b2[,1],
                  up=b2[,2],
                  index=rownames(b2))
 dtn2 <- dt2[-1,]
 ggplot(dtn2,aes(y=index,x=Value,xmin=low,xmax=up)) +
     geom_point() + geom_errorbarh()

```
From the fixed effect coefficeint value plot, we can see that PriceRange2 doesn't have influence on the rating score. Even thou the reveiw_count is significant, however it doesn't really help for predicting the score. 
Among all the ambience factors, except touristy, all other ambience type have positive influence on the score, and touristy has negtive influence. From this we can infer that most of the restaurant with touristy ambience will lower the scores of the restaurant.
Another interesting finding is that, American food would have a negative influence but Breakfast & Brunch would have a positive influence. This might be caught by the diversity of American food restaurant which would also include fast-food.

## Problems and Limitaion
Since the outcome of the stars is ordinal, the model lmer is trying to fit the out come as continues, so we can see the residual plot is not as normal distributed. To improve the model, we need to considerr the the multinomial multilevel mnodels. This model can be implemented in brms package using brm function to choose the family equals to acat("logit"). This can be tried in future modeling. 
```{r}
ggplot(fit_df2)+geom_point()+aes(x=pred,y=resid_pred)+geom_hline(yintercept=0,lty="dashed") +
  ggtitle("Residual Plot")
```



